\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\moderncvstyle{classic}
\moderncvcolor{green}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{ragged2e}

\name{Simone}{Romagnoli}
\title{Cover letter}
\phone[mobile]{+39 347 241 0530}
\email{simone.romagnoli.21@gmail.com}

\newcommand{\company}{JAKALA}
\newcommand{\position}{GCP Data Engineer}
\newcommand{\gap}{ }

\begin{document}
    \recipient{\company}{}
    \date{Milan, \today}

    \opening{\textbf{Application for \position\gap position at \company}
        \\
        \vspace{15pt}
        To the attention of the recruiting team at \company,
    }
    \closing{Sincerely,}

    \makelettertitle

    \justifying
    I am applying as a \textit{\position} because I believe it would be a game-changing experience, enhancing my personal and professional growth.
    I think your mindset built around innovation, curiosity and precision would guide me in the development of my dream career.
    My academic path made me develop a problem-solving and result-oriented attitude that I would like to bring into play, contributing to \company's mission.

    I am very passionate about everything that involves software: it has always fascinated me.
    When I was 4 years young, I got my first personal computer.
    I was so enchanted that I learnt to read and write on my own thanks to it.
    Growing up, I decided to fully embrace this passion by becoming a software engineer.
    \\
    Today, I am a student at the university of Bologna, currently working on my master's degree final thesis in collaboration with Prometeia.
    I joined the latter company as a software engineer intern, and I am working on a data integration project, learning about the Spark technology.
    \\
    Alongside my academic career, I have always worked even within environments unrelated to technology, driven by search for independence.
    As branch leader inside supermarkets, I improved my communication skills and ability to work in a team, showing my dedication, perseverance and commitment.
    As a waiter, I learnt to maintain a positive and optimistic attitude even under pressure, working for customer's satisfaction.

    \company is the company that seeks to overcome impossible challenges, and I want to take part in this process.
    Within your reality, I would be able to fulfill my curiosity and interest in discovering new amazing technologies.
    Your approach towards problem-solving from an engineering standpoint, analyzing problems and designing the best solution in a structured way impressed me.
    My interests revolve around writing secure and reusable software, paying particular attention to task automation.
    Also, I am intrigued by pair programming, the DevOps philosophy and domain-driven design.
    I am looking forward to explore such values in an environment that encourages open debate and diversity.
    In fact, I really appreciate the attention you pay to Spooners, their personal development and working-life balance.
    For all these reasons, I really want to join your culture and create a win-win relationship.

    I would be glad for an opportunity to introduce myself to you in an interview.

    \vspace{0.5cm}

    Thank you for your time and consideration,

    \makeletterclosing

\end{document}


%% end of file `template.tex'.
